New titles are hard to come up with

### 2014-12-12 tex/paper.tex
Add experiment section to paper

>>>>

%-------------------------------------------------------------------------
\section{Experiments}

In the following we present the results of the experiments we performed. The experiments were conducted 
on one of two architectures. The first architecture was composed of a single convolutional and pooling 
layer followed by two fully connected layers. The convolutional layer used 20 filters of size 3x3, 
while the max-pooling layer used non-overlapping windows of size 2x2. The first fully connected layer 
was composed of 150 units, and the final output layer had 10 units (one per label). The second 
architecture added a second set of convolutional and pooling layers before the fully connected layers. 
This added convolutional layer had 800 filters of size 8x8, while the added max-pooling layer also used 
on-overlapping window size of 2x2. The nonlinearity activation function across both architectures and 
all layers was the hyperbolic tangent. A representation of these architectures can be seen in Figure [?].

%-------------------------------------------------------------------------
\subsection{MNIST Dataset}

The following experiments were conducted using the MNIST dataset [?], which includes a training set of 
60000 28x28 handwritten digit images and a test set of 10000 28x28 handwritten digit images. It is important 
to note that both the training and test sets are composed of two sets of digits: an easier set written by 
US Census Bureau employees and a harder set written by high school students.

%-------------------------------------------------------------------------
\subsection{One Convolutional Layer}

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit 
(training set of 500 images), and was subsequently tested on 1000 new images per digit (test set of 10000 images). 
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure [?]. The test accuracy was recorded every five training
iterations. An example classification of an image along with the internal state of the trained network is depicted 
in Figure [?]. Figure [?] shows examples of correctly and incorrectly classified images.

%-------------------------------------------------------------------------
\subsection{Two Convolutional Layers}

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit 
(training set of 500 images), and was subsequently tested on 1000 new images per digit (test set of 10000 images). 
The training images were taken from the easier portion of the training set, while the test images were taken from both sets. 
The results of this training can be seen in Figure [?]. Again, the test accuracy was recorded every five training iterations. 
An example classification of an image along with the internal state of the trained network is depicted in Figure [?]. Figure 
[?] shows examples of correctly and incorrectly classified images.

%-------------------------------------------------------------------------
\subsection{One Convolutional Layer with Larger Training Set}

The second experiment with the one convolutional/pooling layer architecture was also trained for 50 iterations but 
with 100 images per digit instead of 50 (training set of 1000 images). This trained network was then tested on 1000 
new images per digit (test set of 10000 images). The results of this training can be seen in Figure [?]. The test 
accuracy was recorded every five training iterations. Figure [?] shows examples of correctly and incorrectly classified images.
